\Huge Handwritten digit recognition

### 2017-02-07 doc/Paper.tex
Add model description, plot prototype

\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}  % graphics with figure-environment
\usepackage{hyperref}
% colors for hyperlinks
% colored borders (false) colored text (true)
\hypersetup{colorlinks=true,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black}
\usepackage{cite}  % bibliograby
% package for header
\usepackage[automark]{scrpage2}
\pagestyle{scrheadings}
\ihead[]{Handwritten character recognition in MPI}
\ohead[]{\today}
\cfoot[]{\pagemark} 
\setheadsepline[122mm]{0.3mm}
\begin{document}
	\title{
	\Huge Handwritten digit recognition
	}

@@

\vspace{5cm}
\begin{abstract}
We implement a neural network to classify handwritten digits. The training is done in parallel, using MPI. We provide a comparison for model hyper-parameters and for training time vs number of processes. It achieves great accuracy and fast training time. An interactive demo is also presented

\end{abstract}
	\newpage
	\tableofcontents
	\newpage

\section{Problem statement}
\label{sec:problem}
Given a picture of a handwritten digit, label it accordingly 0 - 9.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=8cm]{images/mnist-images.png}
\caption{Sample MNIST images}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=8cm]{images/mnist-matrix.png}
\caption{Matrix representation of a digit}
\end{figure}

\newpage

\bibliographystyle{ieeetr}
	\bibliography{references} % expects file "references.bib"
	\addcontentsline{toc}{section}{References}
\end{document}

>>>>

\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

\usepackage{cite}  % bibliograby
\usepackage{graphicx}  % images
\usepackage{pgfplots}  % plots
  \pgfplotsset{width=10cm,compat=1.9} % plots settings
  \usepgfplotslibrary{external}
  \tikzexternalize

\usepackage{hyperref}  % references
  \hypersetup{colorlinks=true,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black} % references settings

\usepackage[automark]{scrpage2} % heading
  \pagestyle{scrheadings}
  \ihead[]{Handwritten character recognition in MPI} % left header
  \ohead[]{\today} % right header
  \cfoot[]{\pagemark} % footer
  \setheadsepline[122mm]{0.3mm}

\begin{document}
	\title{
	\Huge Handwritten digit recognition
	}

@@

\vspace{5cm}
\begin{abstract}
We implement a neural network to classify handwritten digits. The training is done in parallel, using MPI. We provide a comparison for model hyper-parameters and for training time vs number of processes. It achieves great accuracy and fast training time. An interactive demo is also presented
\end{abstract}

\newpage
\tableofcontents

\newpage
\section{Problem statement}
\label{sec:problem}
Given a picture of a handwritten digit, label it accordingly 0 - 9.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=8cm]{images/mnist-images.png}
\caption{Sample MNIST images \cite{tf}}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=8cm]{images/mnist-matrix.png}
\caption{Matrix representation of a digit \cite{tf}}
\end{figure}

\newpage
\section{Model}
\label{sec:model}
We use a back-propagation neural network with cross-entropy as cost function and soft-max activation. L2 regularization is used to limit overfitting and adaptive learning rate helps soften instability in later epochs.

\begin{figure}[htb]
\centering
\includegraphics[width=8cm]{images/model-graph.png}
\caption{Simplified representation of model graph \cite{tf}}
\end{figure}

\paragraph{Training} We employ gradient-descent on mini-batches. Early-stopping prevents the model from further learning when performance on the validation split starts decreasing.

\paragraph{Evaluation}
TODO

\begin{tikzpicture}
\centering
\begin{axis} [
  title={Training performance},
  xlabel={Epoch},
  ylabel={Accuracy (\%)},
  xmin=0, xmax=100,
  ymin=0, ymax=100,
  xtick={0,25,50,75,100},
  ytick={0,25,50,75,100},
  legend pos=south east,
]

\addplot[]
  coordinates {
  (0,25)(25,65)(50,90)(100,95)
  };
\addplot[dashed]
  coordinates {
  (0,25)(25,50)(50,80)(100,90)
  };

\legend{train set, test set}
\end{axis}
\end{tikzpicture}

\newpage
\bibliographystyle{ieeetr}
	\bibliography{references} % expects file "references.bib"
	\addcontentsline{toc}{section}{References}

\end{document}
